---
title: "LearnR Exercises - Week 09 - Multiple Regression"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(learnrhash)
gradethis::gradethis_setup()

library(tidyverse)
library(broom)
library(texreg)
data(df_opposition) 
```

## Warm-Up

Before we start running regressions with multiple explanatory variables, let's recap why we might want to do this in the first place. As discussed in class, one of the main reasons for multiple regression is to address concerns about omitted variable bias. If present, it implies that we systematically miss the true parameter in the population model when we run our statistical model. 

**Choose the correct statement:**

```{r assumptions_q1, echo = FALSE}
question(sprintf("Is our estimate of $\\beta_1$ biased, if we fail to include a variable that affects our outcome $y$ but is not correlated with $x_1$?"),
  answer("Yes."),
  answer("No.", correct = T),
  random_answer_order = TRUE,
  allow_retry = T,
  incorrect = "Hint: Have a look at the slides on omitted variable bias."
)

```


### Getting to know your data

You are again going to work with the `df_opposition` data that is already preloaded. You are already quite familiar with the data, so hopefully it won't take long for you to answer the following two questions:

**What is the mean share of opposed votes (`conflict_p`) across all opposition parties and countries (in percent and rounded to two meaningful (non-zero) digits (e.g., 0.23, 4.5, 13))?**

```{r mean_conflict_sol, echo = FALSE, eval=FALSE}
mean(df_opposition$conflict_p) %>% round(2)*100
```


```{r mean_conflict, exercise = TRUE}

```


```{r mean_conflict_q, echo = FALSE}
question_text("Enter the mean percentage share of opposed votes rounded to two meaningful digits:",
  answer("56", correct = T),
  answer("0.56", correct = F, message = "Provide your answer in percent."),
  answer("0.55", correct = F, message = "Provide your answer in percent and rounded to two digits."),
  answer("56.66", correct = F, message = "Too detailed. It is not really relevant whether the vote share is 0.01 % higher or lower in substantive terms. Therefore it suffices to report two non-zero digits in this case."),
  allow_retry = T
)
```


**Now that we know the mean share, how many countries have an average opposition score higher than this mean?**

*Hint: Keep in mind how the variable is measured in the data set. It might be helpful to store the average value in a separate object first.*

```{r cntry_conflict_sol, echo = FALSE, eval=FALSE}
avg_opp <- mean(df_opposition$conflict_p)

df_opposition %>% 
  group_by(country) %>% 
  summarise(avg_opposition = mean(conflict_p)) %>% 
  filter(avg_opposition > avg_opp) %>%
  count()
```


```{r cntry_conflict, exercise = TRUE}

```


```{r cntry_conflict_q, echo = FALSE}
question_text("Enter the number of countries with an average opposition score above the mean here:",
  answer("7", correct = T),
  allow_retry = T
)
```

## Multiple Regression

Last week, we found that size of a party (`seatshare`) is associated with an increase in how often a party votes against the government. However, over the course of this week, you couldn't stop thinking about it and started fearing that there may be unobserved factors that confound the relationship between the two variables of interest both at the party level as well as at the system level. 

Specifically, one might expect that larger parties are on average ideologically closer to government parties than smaller (fringe) parties. Moreover, it is possible that larger parties have more government experience and are, therefore, likely to behave differently vis-a-vis the government than smaller parties. 

In addition, there may be party-system specific factors varying between countries that affect how party size and opposition to the government are related in our data. For example, the degree to which institutional arrangements allow opposition parties to influence decision-making, the general openness of the competition structure of a party system, the overall importance of the parliament for policy-making, the type of government the opposition parties are facing, as well as how high the threshold is to record voting behavior may be theoretically plausible factors that affect the relationship between party size and opposition behavior.

Luckily, the data set by Tuttnauer (2018) includes variables that measure these potential confounders:

* `abs_lrdiff`: Ideological distance from the government as the absolute difference between a party's left-right position and the size-weighted average position of the government coalition.
* `ge`:  Government-experience value that ranges between 0 if the party has always been in opposition and 1 if the party has always been in government.
* `inst_power`:  Institutional power of the opposition measuring the strength of the committee system on a scale from 0 to 7.
* `y_openness`: Average number of distinct government compositions in the past 10 years.
* `importance`: Index ranging between 0 (low-importance parliament) and 1 (high-importance parliament).
* `govtype_mod`: A dummy (=1) for surplus coalitions, in contrast with minimal-winning ones (=0).
* `record_threshold`:The percentage of MPs needed to call for a recorded vote (ranging between 0 and 0.3).

**Run a regression of the conflict measure on seat share controlling for the above mentioned confounders.**

```{r lm_1_sol, eval=FALSE, echo = FALSE}
model <- lm(conflict_p ~ abs_lrdiff + seatshare + ge + inst_power + 
              y_openness + importance + govtype_mod + record_threshold, data = df_opposition)
knitreg(model)
```

```{r lm_1, exercise = TRUE}

```

**What is the the size of the estimate for seat share (rounded to two meaningful digits)?**

```{r lm_1_q, echo = FALSE}
question_text(
  "The estimate for seatshare (rounded to two meaningful digits) is:",
  answer("0.57", correct = T),
  answer("57", correct = F, message = "Close, but this time you were supposed to report the actual size of the estimate without transforming it the into percentage share."),
  allow_retry = T
  )
```

### Prediction

Let's use the model to calculate the predicted share of opposed votes for meaningful values that we may be interested in. 

**According to our model, how much more/less do parties with a seat share of 10% oppose the government on average in comparison to a party with a seat share of 30% holding all other variables at their mean/median? Please provide the answer in percent with two significant (non-zero) digits.**

*(Hint: If you stored the regression output in a separate object in the previous task, you are able to access the object here. Alternatively, you can also re-run the regression in this chunk.)*

```{r predict_sol, eval = F, echo = F}
model <- lm(conflict_p ~ abs_lrdiff + seatshare + ge + inst_power + 
              y_openness + importance + govtype_mod + record_threshold, data = df_opposition)

df_scenario <- tibble(
   seatshare = c(0.1, 0.3)
  , abs_lrdiff = mean(df_opposition$abs_lrdiff)
  , ge = mean(df_opposition$ge)
  , inst_power = mean(df_opposition$inst_power)
  , y_openness = mean(df_opposition$y_openness)
  , importance = mean(df_opposition$importance)
  , govtype_mod = median(df_opposition$govtype_mod)
  , record_threshold = mean(df_opposition$record_threshold)
)

predict(model, newdata = df_scenario) %>% round(2)*100
(predict(model, newdata = df_scenario)[1]-predict(model, newdata = df_scenario)[2]) %>% round(2)*100
```

```{r predict, exercise=TRUE, exercise.setup = "lm_1"}

```

```{r predict_q, echo = FALSE}
question_text(
  "The difference in the share of votes opposing the government between parties with a seat share of 10% and 30% is __ percentage points.",
  answer("11", correct = T),
  answer("11.46", correct = F, message = "Close, but this is too detailed. Please provide the answer with two meaningful digits only."),
  answer("0.11", correct = F, message = "Please provide the answer in percentage points."),
  allow_retry = T
)
```

### Categorical/dummy variables

Usually, we should be very carefully interpreting control variables by themselves, at least if we didn't spent much time thinking about potential confounders affecting the relationship between a particular control variable and the outcome of interest. For more details on this topic, check out the overview essay, "The Causal Interpretation of Estimated Associations in Regression Models", by Keele et al. (2019) which is available here: https://doi.org/10.1017/psrm.2019.31


**In this case, however, you are required to make an exception and provide an interpretation of the estimate for `govtype_mod` from the regression model that you ran above.**

*Note that more than one answer can be correct.*

```{r lm2, exercise=TRUE, exercise.setup = "lm_1"}

```

```{r qlm_1_q, echo = FALSE}
question("What does the regression tell us about the relationship between government coalition types (`govtype_mod`) and the share of votes opposed to the government?",
  answer("A one unit increase in `govtype_mode` causes a decrease of about 0.04 percentage points in votes against the government, holding everthing else contant.", correct = F, message = "Be very careful to make causal statements when using regression analysis without a randomization strategy. Moreover, you are dealing with a dummy variable so it is recommendable to provide interpretations for the respective category values."),
  answer("Opposition parties facing a surplus coalition government vote on average 0.04 percentage points more often against the government than opposition parties facing a minimal-winning coalition, holding everthing else contant.", correct = T),
  answer("Opposition parties facing a minimal-coalition government vote on average 0.04 percentage points more often against the government than opposition parties facing a surplus coalition government, holding everthing else contant.", correct = F, message = "Think about the reference category."),
  answer("Opposition parties facing a minimal-coalition government vote against the government in 83% of the votes on average, setting all other variables to zero.", correct = T),
  random_answer_order = TRUE,
  allow_retry = T
)

```

## Submit

```{r context="server"}
learnrhash::encoder_logic()
```

```{r encode, echo=FALSE}
learnrhash::encoder_ui(default_ui(url = "https://ilias.uni-mannheim.de/ilias.php?baseClass=ilObjSurveyGUI&ref_id=1095407&cmd=infoScreen"))
```



